\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Wayne Havey Journal \#5\\
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Wayne R. Havey III}
\IEEEauthorblockA{\textit{PhD Student: Security Track} \\
\textit{UCCS}\\
Colorado Springs, CO \\
whavey@uccs.edu}
}

\maketitle

\section{This Weeks Learning: Survey Paper (cont.)}
\subsection{Introduction}
Not much has happened since the last journal. I made a few tweaks to the initial draft to resubmit in time for the deadline. 
\subsection{Figures}
In the first submission I forgot to include any figures. I spent some time trying to figure out what type of model would best convey the classification model. After the talks in class I think a grid approach may be the best but I still would like to attempt a full logic diagram or automaton type diagram. I drew out by hand the full classification and realized it was difficult to encompass all the subcategories while keeping the figure easily understood. Im thinking about breaking the main diagram into several smaller ones. I made a few diagrams that make up multiple subpieces using draw.io. I may use some figures from related surveys for the sub categories and have my own primary figure. 
\subsection{Other Surveys and continued Reading}
Ive been continuing to search for other surveys because Im often paranoid that Ive just missed one that already conveys my idea. So far there have been a few that are close but nothing I think that would make my idea useless. Most other surveys seems to be trying to teach the reader about the field in general as opposed to really focusing on splitting up papers. Ill continue to read other surveys as I get a lot of good ideas about how to organize some of my sub categories from them.

\end{document}
